---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# extr

The goal of **extr** is to estimate finite-horizon extinction risk from
population time series under a density-independent (drifted Wiener) model,
with support for both naive MLE and observation-error-and-autocovariance-robust
(OEAR) variance estimation.

## Installation

```{r install, eval=FALSE}
# CRAN release
install.packages("extr")

# GitHub version (may be newer than CRAN)
# install.packages("remotes") # if needed
remotes::install_github("hakoyamah/extr")
```

## Main function

### `ext_di()`

`ext_di()` estimates population growth rate, variance, and extinction
probability from a time series of population sizes. It supports two
variance estimators: the default naive maximum-likelihood estimator
(`method = "naive"`) and an
observation-error-and-autocovariance-robust estimator
(`method = "oear"`). Confidence intervals for extinction probability are
based on the $w$-$z$ method.

## Example

The following example uses the Yellowstone grizzly bear time series from
Dennis et al. (1991), digitized from Fig. 5. The published series is a
running 3-year sum (3-year moving total).

```{r load-library}
library(extr)
```

```{r load-data}
dat <- data.frame(
  Time = 1959:1987,
  Population = c(
    44, 47, 46, 44, 46, 45, 46, 40, 39, 39, 42, 44, 41, 40,
    33, 36, 34, 39, 35, 34, 38, 36, 37, 41, 39, 51, 47, 57, 47
  )
)
```

Probability of decline to 1 individual within 100 years:

```{r extinction-1}
ext_di(dat, th = 100)
```

Probability of decline to 10 individuals within 100 years:

```{r extinction-10}
ext_di(dat, th = 100, ne = 10)
```

With QQ plot:

```{r qqplot}
ext_di(dat, th = 100, ne = 10, qq_plot = TRUE)
```

Using the OEAR variance estimator:

```{r oear}
ext_di(dat, th = 100, method = "oear")
```
