---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# extr

The goal of **extr** is to provide tools for estimating extinction probabilities
and confidence intervals for stochastic population models.

## Installation

```{r install, eval=FALSE}
install.packages("extr_1.0.0.tar.gz", repos = NULL, type="source")

# install.packages("remotes") # if needed
remotes::install_github("hakoyamah/extr")
```

## Function

### `ext_di()`

Estimates demographic parameters and extinction probabilities from time series of population sizes based on a Wiener-drift process model. Implements the w-z method (Hakoyama, 2025) to improve the accuracy of confidence intervals over conventional approaches

## Example

```{r load-library}
library(extr)
```

```{r load-data}
dat <- data.frame(Time = c(1959, 1960, 1961, 1962, 1963, 1964, 1965,
1966, 1967, 1968, 1969, 1970, 1971, 1972, 1973, 1974, 1975, 1976,
1977, 1978, 1979, 1980, 1981, 1982, 1983, 1984, 1985, 1986, 1987),
Population = c(44, 47, 46, 44, 46, 45, 46, 40, 39, 39, 42, 44, 41, 40,
33, 36, 34, 39, 35, 34, 38, 36, 37, 41, 39, 51, 47, 57, 47))
```

```{r extinction-1}
ext_di(dat, th = 100)
```

```{r extinction-10}
ext_di(dat, th = 100, ne = 10)
```

```{r qqplot}
ext_di(dat, th = 100, ne = 10, qq_plot = TRUE)
```
