---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# extr

The goal of **extr** is to provide tools for estimating extinction
probabilities and confidence intervals for stochastic population models.

## Installation

```{r install, eval=FALSE}
install.packages("extr_1.0.0.tar.gz", repos = NULL, type = "source")

# install.packages("remotes") # if needed
remotes::install_github("hakoyamah/extr")
```

## Function

### `ext_di()`

Estimates demographic parameters and extinction probability under a
density-independent (drifted Wiener) model. From a time series of
population sizes, it computes MLEs of growth rate and environmental
variance, then evaluates extinction risk over a horizon $t^{\ast}$.
Confidence intervals are constructed by the $w$-$z$ method,
which achieve near-nominal coverage across the full parameter space.

## Example

```{r load-library}
library(extr)
```

```{r load-data}
dat <- data.frame(
  Time = 1959:1987,
  Population = c(
    44, 47, 46, 44, 46, 45, 46, 40, 39, 39, 42, 44, 41, 40,
    33, 36, 34, 39, 35, 34, 38, 36, 37, 41, 39, 51, 47, 57, 47
  )
)
```

```{r extinction-1}
ext_di(dat, th = 100)
```

```{r extinction-10}
ext_di(dat, th = 100, ne = 10)
```

```{r qqplot}
ext_di(dat, th = 100, qq_plot = TRUE)
```

```{r digits-option}
ext_di(dat, th = 100, digits = 9)
```
